\documentclass[a4paper,9pt,final]{scrartcl}
% \documentclass[a4paper,10pt]{scrbook}

\usepackage[utf8]{inputenc}

\usepackage[romanian]{babel}
%\usepackage{german}
\usepackage[left]{eurosym}
\RequirePackage{graphicx}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{array}
\usepackage{multicol}

\setlength{\columnseprule}{20pt}
\setlength{\textwidth}{16cm}
\setlength{\textheight}{23cm}
\setlength{\oddsidemargin}{0cm}

\setlength\parindent{0pt}%Festlegen des Absatzeinzuges

%opening
\title{\textbf{TRANSCRIPT OF RECORDS}\\[0.5em]
Record of study and examination results in the
Bachelor course of Physics
with a Minor in \ergfach}
% \subtitle{foo}
\author{}


\newcommand{\ergfach}{Astrophysics and Electronics}
\newcounter{firstyear} \setcounter{firstyear}{2009}

%%%%%%%%%%%%%% End of Configuration -- Naja, fast...

\newcommand{\mc}[3]{\multicolumn{#1}{#2}{#3}}
\newcommand{\mr}[3]{\multirow{#1}{#2}{#3}}

\newcommand{\first}{\wintersemester{\thefirstyear}}

\newcounter{secondyear} \setcounter{secondyear}{\value{firstyear}} \addtocounter{secondyear}{1}
\newcommand{\second}{\sommersemester{\thesecondyear}}
\newcommand{\third}{\wintersemester{\thesecondyear}}

\newcounter{thirdyear} \setcounter{thirdyear}{\value{firstyear}} \addtocounter{thirdyear}{2}
\newcommand{\fourth}{\sommersemester{\thethirdyear}}
\newcommand{\fifth}{\wintersemester{\thethirdyear}}

\newcounter{fourthyear} \setcounter{fourthyear}{\value{firstyear}} \addtocounter{fourthyear}{3}
\newcommand{\sixth}{\sommersemester{\thefourthyear}}
\newcommand{\seventh}{\wintersemester{\thefourthyear}}

\newcounter{fifthyear} \setcounter{fifthyear}{\value{firstyear}} \addtocounter{fifthyear}{4}
\newcommand{\eigth}{\sommersemester{\thefifthyear}}
\newcommand{\nineth}{\wintersemester{\thefifthyear}}

\newcounter{sixthyear} \setcounter{sixthyear}{\value{firstyear}} \addtocounter{sixthyear}{5}
\newcommand{\tenth}{\sommersemester{\thesixthyear}}
\newcommand{\eleventh}{\wintersemester{\thesixthyear}}

\newcounter{seventhyear} \setcounter{seventhyear}{\value{firstyear}} \addtocounter{seventhyear}{6}
\newcommand{\twelveth}{\sommersemester{\seventhyear}}

\newcommand{\lecture}{L}
\newcommand{\excercise}{E}
\newcommand{\seminar}{S}
\newcommand{\practical}{PC}
\newcommand{\project}{PJ}
\newcommand{\tutorial}{T}

\newcommand{\written}{we}
\newcommand{\writtenterm}{wt}
\newcommand{\oral}{oe}
\newcommand{\pass}{pass}
\newcommand{\assignment}{wa}
\newcommand{\paper}{tp}
\newcommand{\presentation}{gp}


%%%%%%%% Makros von Roland
\def\instead#1#2{\hbox to 0pt{#2\hss}\phantom{#1}}
\newbox\insteadboxi
\newbox\insteadboxii
\newbox\insteadboxiii
\newbox\insteadboxiv
\newbox\insteadboxv
%%%%%%%%%

\newcommand{\sommersemester}[1]{\instead{ W}{ S }#1}
\newcommand{\wintersemester}[1]{ W  #1}

\begin{document}

% \maketitle

\begin{tabular}{llcll}
	
	ROMANIA & \hfill No. 757/31.05.2016 \\
	Ministry of National Education and Scientific Research \\
	University of Bucharest, & 	Faculty of Mathematics and Computer Science \\
	Bachelor Degree in Mathematics \\
	Study program: Mathematics and Computer Science\\
	
	
		
\end{tabular}

\begin{center}
	\begin{Large}TRANSCRIPT OF RECORDS\end{Large}

	\vspace{3em}

	
\end{center}

\begin{tabular}{llcll}
	
	Grades obtained	in scholar time by: &\textbf{COBELI C.I. STEFAN-MATEI} \\
	Date and birth place: & November $16^{th}$ 1994, Rochester, U.S.A.\\
	First and middle names of parents: & Father: Cristian-Ioan, Mother: Elena-Nadia\\
	Personal numeric code: & 194 1116 330 821.
	
	
\end{tabular}
\paragraph{}
TRANSCRIPT OF RECORDS ON PROMOTED YEARS:

\begin{center}
	First year 2013-2014
	\begin{longtable}{|c|m{6cm}|m{1.5cm}|m{1.5cm}|m{1.5cm}|m{1.5cm}|}
		\hline
		No. & Subject of study & First Semester Grades & Second Semester Grades & First Semester ECTS & Second Sem. ECTS\\
		\hline
		\hline
		1. & Algebra & 9 & 10 & 7 & 7 \\ \hline
		2. & Calculus & 8 & 9 & 7 & 7 \\ \hline
		3. & Geometry & 9 & 10 & 7 & 7 \\ \hline
		4. & Mathematical logic and set theory & 10 & - & 5 & -\\ \hline
		5. & Procedural programming & 9 & - & 4 & - \\ \hline
		6. & Algorithms and data structures & - & 9 & - & 4 \\ \hline
		7. & Algorithmic graph theory & - & 10 & - & 5 \\ \hline 
		8. & English & - & 9 & - & 3 \\ \hline		
		\multicolumn{4}{|c|}{Total number of ECTS on first year: 63} & 30 & 33 \\ \hline 
			\multicolumn{6}{c}{} \\ 
			\multicolumn{4}{r}{Promoted, with GPA 9.27 of 10.}
				
	\end{longtable}

\end{center}


\begin{center}
	Second year 2014-2015
	\begin{longtable}{|c|m{6cm}|m{1.5cm}|m{1.5cm}|m{1.5cm}|m{1.5cm}|}
		\hline
		No. & Subject of study & First Semester Grades & Second Semester Grades & First Semester ECTS & Second Sem. ECTS\\
		\hline
		\hline
		1. & Algebra & 9 & 9 & 4 & 4 \\ \hline
		2. & Measure theory & 10 & - & 4 & - \\ \hline
		3. & Differential geometry & 10 & 5 & 4 & 4 \\ \hline
		4. & Differential equations & 5 & - & 5 & -\\ \hline
		5. & Computer architecture & 9 & - & 4 & - \\ \hline
		6. & Operating systems & 6 & - & 5 & - \\ \hline
		7. & Object oriented programming & - & 8 & - & 4 \\ \hline
		8. & Complex analysis & - & 9 & - & 4 \\ \hline 
		9. & Probabilities & - & 6 & - & 4 \\ \hline
		10. & Formal languages and automata theory & - & 10 & - & 4 \\ \hline
		11. & Databases & - & 6 & - & 4 \\ \hline
		12. & Mechanics & - & 6 & - & 4 \\ \hline
		13. & Practice & - & Approved & - & 2 \\ \hline
		14. & English & - & 10 & - & 3 \\ \hline
		\multicolumn{4}{|c|}{Total number of ECTS on second year: 63} & 26 & 37 \\ \hline
			\multicolumn{6}{c}{} \\ 
			\multicolumn{4}{r}{Promoted, with GPA 7.86 of 10.}
				
	\end{longtable}
\end{center}

\newpage

\begin{small}
	Note: The time study period at the Faculty of Mathematics and Computer Science on bachelor degree lasts for
6 (six) semesters. \\
The granted grades are between 1 and 10 and the minimum
pass grade is 5 (five). For the bachelor degree exam the minimum pass grade is 6 (six).
\end{small}

\vspace{50pt}
\paragraph{}
\begin{Large}
	\textbf{Dean,  \hfill Chief Secretary,\\
	Dr. Radu Gramatovici \hfill  Evelina Coteneanu
		}
\end{Large}


\vspace{75pt}
\begin{Large}
\hfill \textbf{Made by secretary,\\
\textit{'} \hfill Adina Dobre}
\end{Large}
\hfill
\newpage

\begin{tabular}{llcll}
	
	ROMANIA & \hfill No. 758/31.05.2016 \\
	Ministry of National Education and Scientific Research \\
	University of Bucharest, & 	Faculty of Mathematics and Computer Science \\
	Address: $14^{th}$ Academiei street, Bucharest, Romania, Postal Code: 70 109 \\
	Phone number: (401) 314 8507\\
	
	
		
\end{tabular}

\begin{center}

	
\hrule \hrule \hrulefill \\
\vspace{10pt}
	\begin{Huge}
		\textbf{Certificate}
	\end{Huge}
	
\end{center}

	The purpose of this Certificate is to certify that mister \textbf{Cobeli C.I. \c Stefan-Matei} (student number 8/2015/Vol.I)  student at the Faculty of Mathematics and Computer Science in the third year (academic year 2015-2016), bachelor degree in Mathematics with specialization on Mathematics and Computer  Science sustained and passed the following exams:
	\begin{itemize}	
		 \item{Number Theory} ($5^{th}$ semester) - 10(ten) - 4 ECTS; 
		 \item{Functional Analysis} ($5^{th}$ semester) - 6(six) - 4 ECTS;
		 \item Partial differential equations ($5^{th}$ semester) - 8(eight) - 4 ECTS;
		 \item Linear optimization ($5^{th}$ semester) - 7(seven) - 3 ECTS;
		 \item Design and analysis of algorithms ($5^{th}$ semester) - 6(six) - 3 ECTS;
		 \item Calculability and complexity ($5^{th}$ semester) - 9(nine) - 3 ECTS;
		 \item Statistics ($5^{th}$ semester) - 8(eight) - 4 ECTS;
		\item Cryptography and coding theory ($5^{th}$ semester) - 10(ten) - 3 ECTS;
		\item Practice ($5^{th}$ semester) - Approved - 2 ECTS;	
	
	\end{itemize}
	

\begin{small}
	Note: The time study period at the Faculty of Mathematics and Computer Science on bachelor degree lasts for
6 (six) semesters. \\
The granted grades are between 1 and 10 and the minimum
pass grade is 5 (five). For the bachelor degree exam the minimum pass grade is 6 (six).
\end{small}
\paragraph{}
This certificate is an annex to the transcript of records with No.757/31/05.2016 ;\\
This certificate was released on the student demand.
\vspace{50pt}
\paragraph{}
\begin{Large}
	\textbf{Dean,  \hfill Chief Secretary,\\
	Dr. Radu Gramatovici \hfill  Evelina Coteneanu
		}
\end{Large}


\vspace{75pt}
\begin{Large}
\hfill \textbf{Made by secretary,\\
\textit{.} \hfill Adina Dobre}
\end{Large}
\hfill
	
\end{document}
